---
title: "STOPS Report"
author: "Amar Sarvepalli"
date: "May 5, 2017"
output: 
  html_document:
    toc: yes
    toc_float: true
    keep_md: yes
    theme: cerulean
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(flexdashboard)
library(dplyr)
library(tidyr)
library(knitr)
library(ggplot2)
library(leaflet)
library(rgdal)
library(plotly)
library(htmltools)
library(DT)
library(chorddiag)
library(readr)
library(DiagrammeR)
```


```{r, echo = FALSE}
# User Settings
#dir <- '/Volumes/C/projects/SMART Plan Systemwide STOPS/AC_MDTEXIST#MDTNOB#MDTBLD_STOPSY2015Results'
dir <- '/Volumes/C/projects/TRB_Apps_2017/Infographic_STOPS/data'

txt_dir <- paste(dir,"txt_extract", sep = "/")
csv_dir <- paste(dir,"csv_dir",sep ="/")

setwd(dir)

options(DT.options = list(
              initComplete = JS("function(settings, json) { ",
                 "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});","}"),
              searchHighlight = TRUE
              ))

```


## 1: Summary of Key Inputs

   Run Parmameters:     1.01
   Station Listing:     1.02
   
------------------------------------------------------------------------------------------------
```{r}
table.name <- "Table     1.01.csv"
x <- read.csv(paste(csv_dir,table.name, sep = "/"))
datatable(x) %>% formatStyle('Run.Parameters', backgroundColor = 'lightgrey')
```

## 2: Summary Of Existing Scenario Results Before Station Group Calibration {.tabset .tabset-fade .tabset-pills}

### 2.01 Initial Calibration Statistics        
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     2.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, caption = "Exsitng Scenario Results Before Station Group Calibration", 
             class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'black')
```

### 2.02 Iter.1 Station Groups by Production District
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     2.02.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, caption = "Station Groups by Production District",
             class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightblue') 
```

### 2.03 Attraction Districts-Station Group Results - Iteration 1
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     2.03.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, caption = "Attraction Districts-Station Group Results",
             class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightgreen')
```

### 2.04 Station Group to Station Group Ridership
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     2.04.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, caption = "Station Group to Station Group Ridership",
             class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'orange')
```

### 2.05 Station Group to Station Group Adj Factors    
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     2.05.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, caption = "Station Group to Station Group Adj Factors",
             class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightpink')
```

------------------------------------------------------------------------------------------------

##  3: Summary Of Station Group Calibration Process 

### Station Group-Station Group Accumulators  {.tabset .tabset-fade .tabset-pills} 
#### 3.01 Station Group to Station Group Ridership-Existing
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     3.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, caption = "Station Group to Station Group Ridership-Existing",
             class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightblue')
```


#### 3.02 Station Group to Station Group Ridership-No-Build
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     3.02.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, caption = "Station Group to Station Group Ridership-No-Build",
             class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightpink')
```

#### 3.03 Station Group to Station Group Ridership-Build
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     3.03.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, caption = "Station Group to Station Group Ridership-Build",
             class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightgreen')
```
   
### Station-Station Accumulators  {.tabset .tabset-fade .tabset-pills} 

#### 3.05 Station Group to Station Group Build Trips
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     3.04.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightblue')
```


#### 3.05 Station Group to Station Group Build Trips (Added by Station Factors)
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     3.05.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightpink')
```

#### 3.06 Station Group to Station Group Project Trips
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     3.06.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'orange')
```

#### 3.07 Station Group to Station Group Project Trips (Added by Station Factors)
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     3.07.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightgreen')
```
  
------------------------------------------------------------------------------------------------

##  4: Summary Of Project Results{.tabset .tabset-fade .tabset-pills}

### 4.01 Weekday Linked District-to-District Transit Trips, Build, All Trips
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     4.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightblue')
```


### 4.02 Weekday Incremental Linked Dist-to-Dist Transit Trips, Build, All Trips
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     4.02.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightpink')
```


### 4.03 Weekday Linked District-to-District Project Trips, Build, All Trips
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     4.03.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'orange')
```


### 4.04 Weekday Unlinked Station-to-Station Project Trips, Build, All Trips
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     4.04.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('StationGroup', backgroundColor = 'lightgreen')
```
    
------------------------------------------------------------------------------------------------

##  5: Summary Of Project Results For Trips On Fixed Guideway (fg) Modes{.tabset .tabset-fade .tabset-pills}

### 5.01 Weekday Linked District-to-District Transit Trips, Build, FG Trips
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     5.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightblue')
```
    
### 5.02 Weekday Incremental Linked Dist-to-Dist Transit Trips, Build, FG Trips
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     5.02.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightpink')
```
    
### 5.03 Weekday Linked District-to-District Project Trips, Build, FG Trips
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     5.03.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'orange')
```
    
### 5.04 Weekday Unlinked Station-to-Station Project Trips, Build, FG Trips
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     5.04.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('StationGroup', backgroundColor = 'lightgreen')
```
       
------------------------------------------------------------------------------------------------

##  6: Summary Of Project Results For Trips Made By 0-car Households{.tabset .tabset-fade .tabset-pills}

### 6.01 Weekday Linked District-to-District Transit Trips, Build, All Trips by 0 Car HH
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     6.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightblue')
```
 
### 6.02 Weekday Incremental Linked Dist-to-Dist Transit Trips, Build, All Trips by 0 Car HH
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     6.02.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightpink')
```
  
### 6.03 Weekday Linked District-to-District Project Trips, Build, All Trips by 0 Car HH
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     6.03.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'orange')
```

### 6.04 Weekday Unlinked Station-to-Station Project Trips, Build, All Trips by 0 Car HH
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     6.04.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('StationGroup', backgroundColor = 'lightgreen')
```
     
------------------------------------------------------------------------------------------------

##  7: Summary Of Project Results For Trips On Fixed Guideway (fg) Modes By 0-car Hh{.tabset .tabset-fade .tabset-pills}

### 7.01 Weekday Linked District-to-District Transit Trips, Build, FG Trips by 0 Car HH
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     7.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightblue')
```
    
### 7.02 Weekday Incremental Linked Dist-to-Dist Transit Trips, Build, FG Trips by 0 Car HH
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     7.02.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightpink')
```
    
### 7.03 Weekday Linked District-to-District Project Trips, Build, FG Trips by 0 Car HH
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     7.03.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'orange')
```
    
### 7.04 Weekday Unlinked Station-to-Station Project Trips, Build, FG Trips by 0 Car HH
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     7.04.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('StationGroup', backgroundColor = 'lightgreen')
```
       
------------------------------------------------------------------------------------------------
##  8: Summary Of Impacts On Automobile Person Miles Of Trips

### 8.01 Incremental District-to-District Vehicle PMT
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     8.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightgreen')
```
 
------------------------------------------------------------------------------------------------

##  9: Comparison Of Existing, No-build And Build Station Boardings By Station Mode Of Access

### 9.01 Average Weekday Station Boardings by Mode of Access
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table     9.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('Station Name', backgroundColor = 'lightgreen')
```
 
------------------------------------------------------------------------------------------------

##  10: Comparison Of Existing, No-build And Build Route Performance {.tabset .tabset-fade .tabset-pills}

### 10.01 Average Weekday Route Boardings
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    10.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('Route Name', backgroundColor = 'lightblue')
```
 
### 10.02 Average Weekday Route Boardings by Station Group
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    10.02.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('Route Name and group', backgroundColor = 'lightpink')
```
 
### 10.03 Peak Route-Level Trips, Miles, and Hours
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    10.03.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('Route Name', backgroundColor = 'orange')
```
 
### 10.04 Off-Peak Route-Level Trips, Miles, and Hours
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    10.04.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('Route Name', backgroundColor = 'lightgreen')
```
    
------------------------------------------------------------------------------------------------

##  11: Summary Of Trips By Submode, Access Mode, Auto Ownership, And Scenario{.tabset .tabset-fade .tabset-pills}

### 11.01 Home-Based Work     
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    11.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('HH Cars', backgroundColor = 'lightblue')
```
   
### 11.02 Home-Based Other   
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    11.02.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('HH Cars', backgroundColor = 'lightpink')
```
   
### 11.03 Non-Home Based     
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    11.03.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('HH Cars', backgroundColor = 'orange')
```
   
### 11.04 Total         
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    11.04.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('HH Cars', backgroundColor = 'lightgreen')
```
   
------------------------------------------------------------------------------------------------

##  12: Summary Of Ctpp Workers And Employees And Mpo Estimates Of Population And Employment By Scenario

### 12.01 SE Summary   
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    12.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'black')
```
  
------------------------------------------------------------------------------------------------

##  13: Summary Of Highway Time, Distance And Speed{.tabset .tabset-fade .tabset-pills}

### 13.01  Existing Time  
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    13.01.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'black')
```
  
### 13.02  No-Build Time  
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    13.02.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'green')
```
  
### 13.03  Build Time   
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    13.03.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'blue')
```
  
### 13.04  Existing Distance
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    13.04.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'lightpink')
```
  
### 13.05  No-Build Distance
```{r, message=FALSE, warning=FALSE, echo = FALSE}
table.name <- "Table    13.05.csv"
x <- read_csv(paste(csv_dir,table.name, sep = "/"))
datatable(x, class = 'cell-border stripe',
             rownames = FALSE) %>% 
  formatStyle('District', backgroundColor = 'orange')
```
  
### 13.06  Build Distance
### 13.07  Existing Speed
### 13.08  No-Build Speed
### 13.09  Build Speed
